\LARGE \bf Geometric Adaptive Control of Attitude Dynamics on $\SO$\\ with State Inequality Constraints

### 2016-02-13 ACC16.2.tex
Add more corrections to long version

\subsection{Attitude Control without disturbance}
We introduce a nonlinear geometric controller for the attitude stabilization of a rigid body.
We first assume that there is no disturbance, i.e., \( \Delta = 0 \).
\begin{prop}[Attitude Control]\label{prop:att_control}
	Given a desired attitude command \( \parenth{R_d, \Omega_d = 0} \), which satisfies the constraint~\cref{eq:constraint}, and positive constants \( k_R, k_\Omega \in \R \) we define a control input \( u \in \R^3 \) as follows
	\begin{gather}
		u = -k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega . \label{eqn:nodist_control}
	\end{gather}
	Then the zero equilibrium of the attitude error is asymptotically stable, and the inequality constraint is satisfied.
\end{prop}

@@

Both control system are able to automatically avoid the constrained regions. 
In addition, these results show that it is straightforward to incorporate an arbitrary amount of large constraints.
In spite of this challenging configuration space the proposed control system offers a simple method of avoiding constrained regions.
These closed-loop feedback results are computed in real time and offer a significant advantage over typical open-loop planning methods.
These results show that the proposed geometric adaptive approach is critical to attitude stabilization in the presence of state constraints and disturbances.
\section{Experiment on Hexrotor UAV}
A hexrotor unmanned aerial vehicle (UAV) has been developed at the Flight Dynamics and Controls Laboratory(FDCL) at the George Washington University~\cite{kaufman2014}.
The UAV is composed of three pairs of counter-rotating propellers. 
%Typical quadrotor UAVs are composed of four or more co-planar propellers.
%As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
%For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
%Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
The propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
%This allows the hexrotor to impart a force in any direction and a moment about any axis.

>>>>

\subsection{Attitude Control without Disturbance}
We introduce a nonlinear geometric controller for the attitude stabilization of a rigid body.
We first assume that there is no disturbance, i.e., \( \Delta = 0 \).
\begin{prop}[Attitude Control]\label{prop:att_control}
	Given a desired attitude command \( \parenth{R_d, \Omega_d = 0} \), which satisfies the constraint~\cref{eq:constraint}, and positive constants \( k_R, k_\Omega \in \R \) we define a control input \( u \in \R^3 \) as follows
	\begin{gather}
		u = -k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega . \label{eqn:nodist_control}
	\end{gather}
	Then the zero equilibrium of the attitude error is asymptotically stable, and the inequality constraint is satisfied.
\end{prop}

@@

Both control system are able to automatically avoid the constrained regions. 
In addition, these results show that it is straightforward to incorporate an arbitrary amount of large constraints.
In spite of this challenging configuration space the proposed control system offers a simple method of avoiding constrained regions.
These closed-loop feedback results are computed in real time and offer a significant advantage over typical open-loop planning methods.
These results show that the proposed geometric adaptive approach is critical to attitude stabilization in the presence of state constraints and disturbances.
\section{Experiment on Hexrotor UAV}
A hexrotor unmanned aerial vehicle (UAV) has been developed at the Flight Dynamics and Controls Laboratory (FDCL) at the George Washington University~\cite{kaufman2014}.
The UAV is composed of three pairs of counter-rotating propellers. 
%Typical quadrotor UAVs are composed of four or more co-planar propellers.
%As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
%For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
%Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
The propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
%This allows the hexrotor to impart a force in any direction and a moment about any axis.
